Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-05-23 article.rnw
Add some numbers to emphasise the atrocious algorithmic complexity of the method.

One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species. %DBS: Add in the number of models for both of these to emphasise the point.
As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.

>>>>

One possible explanation is that species simply do not group to the same extent in a quantitative competitive context as in a binary network.
That said, the results suggest that this is unlikely as grouping was still likely to increase parsimony.
Further, there is no reason to suspect that species would not have clear similarities or dissimilarities in their ecological niches, and therefore their competitive effects and responses \parencite{XXX}.
In the present case, we cannot rule out the possibility that a lack of clarity in the groupings is instead a product of the study system.
All the species in this study were members of the same genus, \emph{Drosophila}, and as such were all rather similar.
A study system with species spanning multiple functional groups, or a broader taxonomy, might have shown clearer groupings.
Alternatively, the small number of species in the study might not have been sufficient for clear groups to be defined.
Alas, the brute force method we employed in this study has a very poor algorithmic complexity, preventing the application of the method to studies with more than seven or eight species (there are ${\left(B_7\right)}^2 = \num{\Sexpr{numbers::bell(7)^2}}$ possible models with $7$ species and ${\left(B_8\right)}^2 = \num{\Sexpr{numbers::bell(8)^2}}$ models with $8$ species).
As such, a better method would be required in order to test for grouping of species interactions among a larger set of species.
